
```{r setup, include=FALSE, echo=FALSE  }
library(knitr)
opts_chunk$set(
	       warning=FALSE, 
	       comment=NA,
	       message=FALSE)
```


Now i am  startign to replicate daniel hadely code found [here](http://danielphadley.com/ggplot-Logo/)



here we go


let' first load the required libraries

```{r libs  }
library(ggplot2)
library(magick)
library(magrittr)
```

Let's make the ggplot first


```{r ggp  }
ggplot(mpg, aes(displ, hwy, colour = class)) + 
  geom_point() + 
  ggtitle("Cars")  + 

  ggsave(filename=paste0("./FIGURES/",last_plot()$labels$title,".png"),
	width=5, height=4, dpi=300 
	 )
```

Now time to read the saved image

```{r si  }
plot <- image_read("./FIGURES/Cars.png")
```

Now let's bring in a logo

```{r lg  }
logo_raw <- image_read("http://hexb.in/hexagons/ggplot2.png") 
```

now i will show different transformation, it could have been done in one go by piping but went ahead and did it break down for better understanding

first up scaling

```{r sc  }
logo_raw %>% 
    image_scale("100") %>% 
    image_display()
```

basically the above will rescale the image into width of 100px and height will change accordingly



now changing the background

```{r bc  }
logo_raw %>% 
    image_background("grey", flatten=TRUE) %>% 
    image_display()
```




